Social Visual Analytics: DevOps for Data Scientists

### 2015-01-30 conclusion.tex
yes

We presented a case for an environment that supports the entire
visual analytics work process, from data acquisition and exploratory
data analysis through development and production deployment. One might
think of this approach as ``DevOps for data science.'' The environment
supports collaboration and communication with capabilities for
creating and sharing experimental workbooks, version control,
searching, recommending, annotating, and deploying experiments
as web sites and as reusable services.

We implemented these ideas in the RCloud prototype.
Experience with the prototype provides evidence that data
science teams, and the organizations in which they work,
benefit from having such capabilities.

Next steps are to support cross-language development, to incorporate
richer source code analysis and recommendation techniques, and
to make improvements in the HTML5 human interface.

>>>>

We presented a case for an environment that supports the visual
analytics process, from data acquisition and exploratory
data analysis, through development and deployment. One might
think of this approach as ``DevOps for data science.''
The environment supports collaboration and communication
with capabilities for creating and sharing experimental workbooks,
version control, searching, recommending, annotating, and publishing
experiments as web sites and as reusable services.

We implemented these ideas in the RCloud prototype.

Experience with the prototype provides evidence that data
science teams, and the organizations in which they work,
benefit from having such capabilities.

Some possible next steps are to support cross-language development,
to incorporate richer source code analysis and recommendation
techniques, to provide fine-grained security, and to improve
the usability of the HTML5 human interface.

### 2015-01-30 introduction.tex
yes

Consider the role of a data science team within an organization today.
Analysts work in loose or tight collaboration with colleagues.
Project teams vary in size, from just a few people to dozens or
more, even within one project's duration. Tasks are broad, including problem
identification, data wrangling, visualization, modeling and analysis,
interpreting, explaining and advocating the results, and often helping
clients to realize the benefits of the work in ongoing processes.
There are many details to these tasks.
For example, data wrangling can involve finding data, figuring out its
syntax and semantics, assessing data quality, performing normalization and
data quality remediation, and making the data available for other tasks
to follow.

@@

\stephen{We could now tell them what we're going to tell them here, but I'm
not sure that's a good approach - unless we feel the reader is having
trouble following the path we are laying out, it seems to disrupt the
flow of the discussion.}

>>>>

Over fifty years ago, John Tukey published ``The Future of Data Analysis''
in which he defined a remarkably prescient agenda for the future of
data analysis and statistical computing. His vision has been realized
through environments like S and R, that fostered the adoption of
statistical graphics and robust techniques for practical data modeling.
The software that we use today has fulfilled his brilliant vision for
the practice of computational data analysis by individual experts.

The field has now moved beyond the boundaries of what Tukey originally
foresaw. Processing and networking capabilities today far exceed
what was only imagined fifty years ago. Cheap, highly parallel
virtualized systems allow analysts to routinely solve problems
involving millions or even billions of data values. Computer
systems today also enable collaboration and the automation of
complex tasks and processes in ways that were hardly even considered
fifty years ago. We turn our attention to this opportunity to
use computation to support data science teams and the visual
analytics process.

As a starting point, consider the role of a data science team within
an organization today.
Analysts work in loose or tight collaboration with colleagues.
Project teams vary in size, from just a few people to dozens or
more, even within one project's duration. Assignments are often
broad, including problem identification, data wrangling, modeling and analysis,
visualization, summarizing and interpreting results, and explaining and advocating
them within the organization, helping clients to realize the benefits of the work.
Eventually, the knowledge or working prototypes created by data science teams
may be transferred to other organizations to employ them in production.
There are many details to all these tasks.  For example, data wrangling can involve
finding data, understanding its syntax and semantics, assessing data quality,
performing normalization and data quality remediation, and making the data available
for the other tasks that will follow.

@@

\stephen{We could tell them what we're going to tell them here, but I'm
not sure that's good - unless we feel the reader will have trouble following
the path we are setting, it seems to disrupt the flow of the discussion.}
